Meta-analysis of gut microbiome studies identifies disease-specific and shared responses

### 2018-12-10 meta-analysis/manuscript.tex
Remove declarations
For some reasons this registers as changing every line of text in the
document. Not sure what's going on, but the only changes in this
commit are just removing the \documentclass and \begin{document}
commands, as well as commenting out the packages.

\documentclass{article}

\usepackage[colorlinks=true]{hyperref} % for links and urls
\usepackage{amsmath,amssymb} % for math
\usepackage{color,soul} % for highlighting
\usepackage{booktabs,rotating,multirow} % for nice tables
\usepackage{authblk} % for author affiliations
\usepackage{graphicx} % for figures
\usepackage[numbers]{natbib}
\usepackage[superscript,biblabel]{cite} % for superscript citations
\usepackage[above]{placeins} % for FloatBarrier
\usepackage{amsmath} % for pretty fraction text (heatmap caption)
\usepackage{lineno} % for line numbers
\usepackage{geometry} % for supp fig large pages

% Change margins
 \geometry{
 left=1.25in,
 right=1.25in,
 top=1in,
% tmargin=0.5in,
% bottom=0.5in
 }

% Smaller captions
\usepackage[font=footnotesize]{caption}

\begin{document}

\title{Meta-analysis of gut microbiome studies identifies disease-specific and shared responses}
\author[1,2]{Claire Duvallet}
\author[1,2,3]{Sean M. Gibbons}
\author[1,2,3]{Thomas Gurry}
\author[4,5]{Rafael A. Irizarry}
\author[1,2,3,*]{Eric J. Alm}
\affil[1]{Department of Biological Engineering, Massachusetts Institute of Technology, Cambridge, MA 02139 USA}
\affil[2]{Center for Microbiome Informatics and Therapeutics, Cambridge, MA 02139 USA}
\affil[3]{The Broad Institute of MIT and Harvard, Cambridge, MA 02139 USA}
\affil[4]{Department of Biostatistics and Computational Biology, Dana-Farber Cancer Institute, Boston, MA 02215 USA}
\affil[5]{Department of Biostatistics, Harvard T.H. Chan School of Public Health, Boston, MA 02115 USA}
\affil[*]{Corresponding author, ejalm@mit.edu}

\maketitle

>>>>

%\usepackage[colorlinks=true]{hyperref} % for links and urls
%\usepackage{amsmath,amssymb} % for math
%\usepackage{color,soul} % for highlighting
%\usepackage{booktabs,rotating,multirow} % for nice tables
%\usepackage{authblk} % for author affiliations
%\usepackage{graphicx} % for figures
%\usepackage[numbers]{natbib}
%\usepackage[superscript,biblabel]{cite} % for superscript citations
%\usepackage[above]{placeins} % for FloatBarrier
%\usepackage{amsmath} % for pretty fraction text (heatmap caption)
%\usepackage{lineno} % for line numbers
%\usepackage{geometry} % for supp fig large pages

%% Smaller captions
%\usepackage[font=footnotesize]{caption}
